### 2018-07-16 manuscript.rmd
incorporating physignals, AICc, model adequacy, Rphylip

```{r setup, include=FALSE}
	# Load packages
	## General
library(knitr)
library(tidyverse)
library(reshape2)
	## Graphics
library(FactoMineR)
library(factoextra)
	## Biological
library(vegan)
library(ape)
library(phangorn)
library(phytools)
library(OUwie)
library(picante)
library(geiger)
library(phylobase)
library(fields)
library(phylosignal)
library(geomorph)
library(phylopath)
library(Rphylip)
library(arbutus)

@@

1.05 Plate with all the tentillum diversity.
1.1 Table showing each character’s (illustrating the character per row)  the phylogenetic signal K with the p-value obtained by testing against 1000 simulated permutations, and the number of species included.
1.2 Table showing the best AICc supported model generating the data for each character and its AICc score. Model adequacy.
1.3 Table/figures showing the reconstructed ancestral values at the internal nodes of the phylogeny of characters with a supported phylogenetic model of evolution.
1.4 Figure showing major categorical character shifts, gains, and losses on a simplified phylogeny.
2 -- COMPARATIVE ANALYSES
2.0 Confusion matrix table showing PIC_correlations and trait correlation R2 and p-values for each pair of continuous characters. Confusion matrix for quantitative and categorical characters GLS. pGLS estimation of regression parameters in significantly correlated pairs.
2.1 Table showing the model parameters for each significant regression.
2.3 Verbally PCA and phylogenetic PCA/PICVarA_PCA of the characters. Phylomorphospace superimposed to the tip coordinates in PC1--PC2.
2.4 Table showing normalized rates of evolution for each character BAMM.
3 -- RELATIONSHIPS WITH DIET / FUNCTION / Hypothesis testing

>>>>

```{r setup, include=FALSE}
	# Load packages
	## General
library(knitr)
library(tidyverse)
library(reshape2)
	## Graphics
library(FactoMineR)
library(factoextra)
library(corrplot)
	## Biological
library(vegan)
library(ape)
library(phangorn)
library(phytools)
library(OUwie)
library(picante)
library(geiger)
library(phylobase)
library(fields)
library(phylosignal)
library(geomorph)
library(phylopath)
library(Rphylip)
library(arbutus)

@@

1.05 Plate with all the tentillum diversity.
1.1 Table showing each character’s (illustrating the character per row)  the phylogenetic signal K with the p-value obtained by testing against 1000 simulated permutations, and the number of species included.
```{r phylosignals}
phylosignals = as.data.frame(matrix(ncol=3, nrow=ncol(sharedmean_logs[,-1])))
names(phylosignals) = c("K", "P", "Ntaxa")
for(i in 2:ncol(sharedmean_logs)){
  CH_I=as.numeric(sharedmean_logs[,i])
  names(CH_I) = rownames(sharedmean_logs)
  SE_I = as.numeric(castSE[,i])
  names(SE_I) = castSE$Species
  CH_I= CH_I[!is.na(CH_I)]
  SE_I= SE_I[!is.na(SE_I)]
  SE_I = SE_I[which(names(SE_I)%in%names(CH_I))]
  CH_I = CH_I[which(names(CH_I)%in%names(SE_I))]
  treeI = drop.tip(ultram,which(!(ultram$tip.label %in% names(CH_I))))
  #print(names(sharedmeans)[i]);print(phylosig(treeI, CH_I, se = SE_I, test=T) %>% .[c("K","P")])
  rownames(phylosignals)[i-1] <- names(sharedmean_logs)[i]
  PSIG <- phylosig(treeI, CH_I, se = SE_I, test=T)
  phylosignals[i-1,1] <- PSIG$K
  phylosignals[i-1,2] <- PSIG$P
  phylosignals[i-1,3] <- length(CH_I)
}
write.csv(phylosignals, "PhylosignalsWSE_log.csv")
```

1.2 Table showing the best AICc supported model generating the data for each character and its AICc score. Model adequacy.

```{r fitContinuous}
#Model support
  Q_sharedmean_logs$Heteroneme_to_CB[which(Q_sharedmean_logs$Heteroneme_to_CB > 9)] <- NA
  AICdf = as.data.frame(matrix(ncol=6,nrow=ncol(Q_sharedmean_logs)))
  colnames(AICdf) = c("Variable", "white_noise", "starBM", "BM", "EB", "OU")
  for(c in 1:ncol(Q_sharedmean_logs)){
    startree <- rescale(ultram, "lambda", 0)
    C = Q_sharedmean_logs[,c]
    names(C) = rownames(Q_sharedmean_logs)
    C = C[!is.na(C)]
    Ctree = drop.tip(ultram, which(!(ultram$tip.label %in% names(C))))
    startree = drop.tip(startree, which(!(startree$tip.label %in% names(C))))
    Cse = castSE[,c+1]
    names(Cse) = castSE$Species
    Cse = Cse[which(names(Cse) %in% names(C))]
    model_matrix = matrix("NA", nrow = 5, ncol = 3)
    colnames(model_matrix) = c("aicc","aicc_best","dAICc")
    row.names(model_matrix) = c("white", "starBM", "BM", "EB", "OU")
    for(j in 1:dim(model_matrix)[1]){
      if(j==2){
        temp_model = fitContinuous(startree, C, model="BM", SE = Cse)$opt
      }
      else{
        temp_model = fitContinuous(Ctree, C, model=row.names(model_matrix)[j], SE = Cse)$opt
      }
      model_matrix = apply(model_matrix,2, as.numeric)
      row.names(model_matrix) = c("white", "starBM", "BM", "EB", "OU")
      model_matrix[j, "aicc"] <- temp_model$aicc
    }
    model_matrix[,"aicc_best"] <- min(model_matrix[,"aicc"])
    model_matrix[,"dAICc"] <- model_matrix[, "aicc"] - model_matrix[j, "aicc_best"]
    print(names(Q_sharedmean_logs)[c])
    string_c <- c(names(Q_sharedmean_logs)[c], model_matrix[,3])
    names(string_c) = colnames(AICdf)
    AICdf[c,] <- string_c
  }
  AICdf[,2:6] = apply(AICdf[,2:6], 2, as.numeric) %>% apply(2, round3)
  write.csv(AICdf, "log_model_support.csv")

#Model adequacy
  worthy_models = AICdf[which(AICdf$white_noise != 0 & AICdf$starBM != 0),]
  MAD = as.data.frame(matrix(ncol = 6, nrow = nrow(worthy_models)))
  names(MAD) = c("msig", "cvar", "svar", "sasr", "shgt", "dcfd")
  rownames(MAD) = worthy_models$Variable
  for(m in 1:nrow(worthy_models)){
    C = Q_sharedmean_logs[,which(names(Q_sharedmean_logs) == worthy_models$Variable[m])]
    names(C) = rownames(Q_sharedmean_logs)
    C = C[!is.na(C)]
    Ctree = drop.tip(ultram, which(!(ultram$tip.label %in% names(C))))
    C = C[match(Ctree$tip.label, names(C))]
    class(Ctree)="phylo"
    FC <- fitContinuous(Ctree,C,model=worthy_models$Best_model[m])
    UTC <- make_unit_tree(FC)
    picstat_data <- calculate_pic_stat(UTC)
    sim <- simulate_char_unit(UTC)
    picstat_sim <- calculate_pic_stat(sim)
    compare_pic_stat(picstat_data, picstat_sim) %>% .$p.values -> MAD[m,]
  }
  phy_models = data.frame(worthy_models,MAD)
  phy_models[,8:13] = apply(phy_models[,8:13], 2,round3)
```
1.3 Figure showing major categorical character shifts, gains, and losses on a simplified phylogeny.

2 -- COMPARATIVE ANALYSES
2.0 Confusion matrix table showing PIC_correlations and trait correlation R2 and p-values for each pair of continuous characters. Confusion matrix for quantitative and categorical characters GLS. pGLS estimation of regression parameters in significantly correlated pairs.
```{r character_correlations, include=FALSE}
C = sharedmatrix[,c(-1,-3)] %>% .[which(!is.na(rowSums(.[,-1]))),]
Cspecies = C$Species %>% as.character()
C = as.matrix(C[,-1])
rownames(C) = Cspecies
Ctree = drop.tip(ultram,which(!(ultram$tip.label %in% rownames(C))))
class(Ctree) = "phylo"
PICi = Rcontrast(Ctree, C, path="phylip-3.695/exe")

2.1 Table showing the model parameters for each significant regression.
2.3 Verbally PCA and phylogenetic PCA/PICVarA_PCA of the characters. Phylomorphospace superimposed to the tip coordinates in PC1--PC2.
2.4 Table showing normalized rates of evolution for each character BAMM.
3 -- RELATIONSHIPS WITH DIET / FUNCTION / Hypothesis testing
